Supporting Information : Effect of copula on extinction risk

### 2019-02-25 SuppMat.Rmd
age str res: linear, nonlinear with extreme tail added

numsims<-10000
numsteps<-100
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-Inf

ktau<-0.6  # kendall's tau

@@

@@

```{r sim_ricker, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

tempo<-paste("./Results/",model,sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")

@@

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_ricker_extrisk_d0, echo=F,results="hide"}
set.seed(seed)

ricker_extrisk_d0<-readRDS("./Results/ricker/ricker_extrisk_d0.RDS")
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims

@@

pdf("./Results/ricker/ricker_extrisk_d0.pdf",height = 6,width=6)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_local_disp}](./Results/ricker/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ricker/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_d0}](./Results/ricker/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_hassell, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

tempo<-paste("./Results/",model,sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
rc_hassell<-((b/(b-1)))^b # transition from under to overcompensatory dynamics
r_bf_hassell<- ((b/(b-2)))^b # bifurcation parameter stable to unstable eqm

@@

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_hassell_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
hassell_extrisk_d0<-readRDS("./Results/hassell/hassell_extrisk_d0.RDS")

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/hassell/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/hassell/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199); numlocs=5, numsteps=25, numsims=10000\label{fig_hassell_risk_d0}](./Results/hassell/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_msmith, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_msmith_extrisk_d0, echo=F,results="hide"}
set.seed(seed)

@@

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231659,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

```{r sim_pennycuick, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"

tempo<-paste("./Results/",model,sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")

numsims<-10000
numsteps<-25
numlocs<-5
a<-a_pennycuick
b<-b_pennycuick
scl<-1

@@

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_pennycuick_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
pennycuick_extrisk_d0<-readRDS("./Results/pennycuick/pennycuick_extrisk_d0.RDS")

@@

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000\label{fig_pennycuick_risk_d0}](./Results/pennycuick/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_verhulst, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-3

@@

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

```{r fig_verhulst_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

>>>>

numsims<-10000
numsteps<-100
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-Inf
ktau<-0.6  # kendall's tau

@@

```{r sim_agestr_with_extremetail_linear, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("ext_risk_cop_age_str.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("ext_risk_cop_age_str.R")
source("ExtremeTailDep.R")
numsims<-10000
numsteps<-100
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-Inf

# For extreme right tail dep.
mr<-retd(n = (numsteps*numsims),d = 2,rl =1,mn=0,sdev=1)
cop<-pnorm(mr) # to make normal to uniformly distributed
 tempo<-paste("./Results/age_str_results/extreme_right_taildep_linear")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
pdf(paste(resloc,"extreme_right_tail_cop.pdf",sep=""),height = 5,width=5)
plot(cop[,1],cop[,2])
dev.off()
las_exR<-sim_age_str(p0=p0,ext_thrs = ext_thrs,cop=cop,par_dist = par_dist,omg=omg,
            numsims = numsims,numsteps = numsteps,ploton=T,resloc=resloc)
saveRDS(las_exR,paste(resloc,"sim_age_str_extreme_right_taildep.RDS",sep=""))

# For extreme left tail dep.
ml<-retd(n = (numsteps*numsims),d = 2,rl =-1,mn=0,sdev=1)
cop<-pnorm(ml) # to make normal to uniformly distributed
 tempo<-paste("./Results/age_str_results/extreme_left_taildep_linear")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
pdf(paste(resloc,"extreme_left_tail_cop.pdf",sep=""),height = 5,width=5)
plot(cop[,1],cop[,2])
dev.off()
 las_exL<-sim_age_str(p0=p0,ext_thrs = ext_thrs,cop=cop,par_dist = par_dist,omg=omg,
            numsims = numsims,numsteps = numsteps,ploton=T,resloc=resloc)
saveRDS(las_exL,paste(resloc,"sim_age_str_extreme_left_taildep.RDS",sep=""))
```

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

![Extinction risk from one patch linear age structured model (omg=Infinity), fecundity of adults and survival of eggs have either extreme left or extreme right tail dep. copula structure, numsims=10000.\label{fig_extrisk_lagestr_extremetail}](./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf){ width=40%, height=40% }

```{r sim_agestr_with_extremetail_nonlinear, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("ext_risk_cop_age_str.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("ext_risk_cop_age_str.R")
source("ExtremeTailDep.R")
numsims<-10000
numsteps<-100
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-100
# For extreme right tail dep.
mr<-retd(n = (numsteps*numsims),d = 2,rl =1,mn=0,sdev=1)
cop<-pnorm(mr) # to make normal to uniformly distributed
 tempo<-paste("./Results/age_str_results/extreme_right_taildep_nonlinear")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
pdf(paste(resloc,"extreme_right_tail_cop_omg_",omg,".pdf",sep=""),height = 5,width=5)
plot(cop[,1],cop[,2])
dev.off()
nlas_exR<-sim_age_str(p0=p0,ext_thrs = ext_thrs,cop=cop,par_dist = par_dist,omg=omg,
            numsims = numsims,numsteps = numsteps,ploton=T,resloc=resloc)
saveRDS(nlas_exR,paste(resloc,"sim_age_str_extreme_right_taildep.RDS",sep=""))
 # For extreme left tail dep.
ml<-retd(n = (numsteps*numsims),d = 2,rl =-1,mn=0,sdev=1)
cop<-pnorm(ml) # to make normal to uniformly distributed
 tempo<-paste("./Results/age_str_results/extreme_left_taildep_nonlinear")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
pdf(paste(resloc,"extreme_right_tail_cop_omg_",omg,".pdf",sep=""),height = 5,width=5)
plot(cop[,1],cop[,2])
dev.off()
nlas_exL<-sim_age_str(p0=p0,ext_thrs = ext_thrs,cop=cop,par_dist = par_dist,omg=omg,
            numsims = numsims,numsteps = numsteps,ploton=T,resloc=resloc)
saveRDS(nlas_exL,paste(resloc,"sim_age_str_extreme_left_taildep.RDS",sep=""))
```

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

![Extinction risk from one patch non-linear age structured model (omg=100), fecundity of adults and survival of eggs have either extreme left or extreme right tail dep. copula structure, numsims=10000.\label{fig_extrisk_nlagestr_extremetail}](./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_100.pdf){ width=40%, height=40% }

@@

```{r sim_ricker_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

@@

```{r fig_ricker_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_ricker_extrisk_d0_scl_1, echo=F,results="hide"}
set.seed(seed)

ricker_extrisk_d0<-readRDS(paste(resloc,"ricker_extrisk_d0.RDS",sep=""))
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=6,width=6)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker__risk_global_disp}](./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_d0}](./Results/ricker_scl_1/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_hassell_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1

rc_hassell<-((b/(b-1)))^b # transition from under to overcompensatory dynamics
r_bf_hassell<- ((b/(b-2)))^b # bifurcation parameter stable to unstable eqm

@@

```{r fig_hassell_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_hassell_extrisk_d0_scl_1, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
hassell_extrisk_d0<-readRDS(paste(resloc,"hassell_extrisk_d0.RDS",sep=""))

@@

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199, scl=1); numlocs=5, numsteps=25, numsims=10000\label{fig_hassell_risk_d0}](./Results/hassell_scl_1/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_msmith_scl_0.8, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

```{r fig_msmith_scl_0.8, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_msmith_extrisk_d0_scl_0.8, echo=F,results="hide"}
set.seed(seed)

@@

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
set.seed(seed)
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231659,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

```{r sim_pennycuick_scl_1, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"
scl<-1

numsims<-10000
numsteps<-25
numlocs<-5
a<-a_pennycuick
b<-b_pennycuick

xx<-diff(rlist)
vxx<-var(xx)
if(vxx>1e-10){
  warning("Not equal spacing in rlist : Pennycuick model !!!",immediate.=T,call.=T)
}

```{r fig_pennycuick_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

```{r fig_pennycuick_extrisk_d0_scl_1, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
pennycuick_extrisk_d0<-readRDS(paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_pennycuick_risk_d0}](./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }

```{r sim_pennycuick_scl_0.6, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"
numsims<-10000
numsteps<-25
numlocs<-5
a<-a_pennycuick
b<-b_pennycuick
scl<-0.6

@@

```{r fig_pennycuick_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_pennycuick_extrisk_d0_scl_0.6, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
pennycuick_extrisk_d0<-readRDS(paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))

@@

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick_scl_0.6/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick_scl_0.6/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000, scl=0.6\label{fig_pennycuick_risk_d0}](./Results/pennycuick_scl_0.6/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_verhulst_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-1

@@

```{r fig_verhulst_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

@@

```{r fig_verhulst_extrisk_d0_scl_1, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.4,0.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_1}](./Results/verhulst_scl_1/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }
